2024 US Presidential Election Forecast Model

### 2024-11-04 paper/paper.qmd
update paper.qmd

```{r}
#| label: Distribution of Percentage
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Percentage", x = "Percentage (%)", y = "Frequency") +
  theme_minimal()
```

## Predictors variable
The transparency score is a predictor variable that reflects the level of openness, honesty, and accessibility perceived in a candidate’s campaign or governance approach. This score typically evaluates factors like the availability of public records, clarity in policy positions, accountability to voters, and the perceived integrity of the candidate. Higher transparency scores generally suggest a campaign or candidate who is more forthcoming with information and responsive to public scrutiny, which can enhance public trust. However, transparency does not always translate to higher support; it may appeal to certain voter demographics while alienating others who prioritize different traits, such as assertiveness or policy efficiency. In the models for both Trump and Harris, transparency score showed different effects, indicating it might play a nuanced role in influencing overall voter support and trust in each candidate’s leadership style.
```{r}
#| label: fig-distribution_transparency_score
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = transparency_score)) +
  geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
  labs(title = "Distribution of transparency score", x = "transparency score", y = "Frequency") +
  theme_minimal()
```

@@

```{r}
#| label: Poll Score by Sample Size and Transparency Score
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = sample_size, y = pollscore)) +
  geom_point(aes(color = transparency_score)) +
  facet_wrap(~ numeric_grade) +
  labs(title = "Poll Score by Sample Size and Transparency Score", x = "Sample Size", y = "Poll Score", color = "Transparency Score") +
  theme_minimal()
```

>>>>

```{r}
#| label: fig-percentage
#| fig-cap: Distribution of Percentage
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = pct)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(x = "Percentage (%)", y = "Frequency") +
  theme_minimal()
```

## Predictors variable
The transparency score is a predictor variable that reflects the level of openness, honesty, and accessibility perceived in a candidate’s campaign or governance approach. This score typically evaluates factors like the availability of public records, clarity in policy positions, accountability to voters, and the perceived integrity of the candidate. Higher transparency scores generally suggest a campaign or candidate who is more forthcoming with information and responsive to public scrutiny, which can enhance public trust. However, transparency does not always translate to higher support; it may appeal to certain voter demographics while alienating others who prioritize different traits, such as assertiveness or policy efficiency. In the models for both Trump and Harris, transparency score showed different effects, indicating it might play a nuanced role in influencing overall voter support and trust in each candidate’s leadership style.

```{r}
#| label: fig-distribution_transparency_score
#| fig-cap: Distribution of transparency score
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = transparency_score)) +
  geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
  labs(x = "transparency score", y = "Frequency") +
  theme_minimal()
```

@@

```{r}
#| label: fig-poll_score
#| fig-cap: Poll Score by Sample Size and Transparency Score
#| echo: false
#| warning: false
#| message: false
ggplot(cleaned_data, aes(x = sample_size, y = pollscore)) +
  geom_point(aes(color = transparency_score)) +
  facet_wrap(~ numeric_grade) +
  labs(x = "Sample Size", y = "Poll Score", color = "Transparency Score") +
  theme_minimal()
```
